Learning with misspecified models: Overconfidence and Stereotypes"  # nolint: Grammarly.

### 2023-09-11 Paper/draft.Rmd
alpha estimate

By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
previous section and allows for direct comparison of all the theories. For realizations of $(\theta, \omega)$ for which there are 
self-confirming equilibria, the dogmatic agent will fall into the 
trap whereas the switcher will be able to escape it. Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading
them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
laboratory experiment. \footnote{because the setting does not match that of @Heidhues2018, there will be situationf for which the theory 
does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
the details of how this example was implemented in the lab.

@@

>>>>

By including self-confirming equilibria, the example captures the forces from each of the updating mechanisms discussed in the 
previous section and allows for direct comparison of all the theories. For realizations of $(\theta, \omega)$ for which there are 
self-confirming equilibria, the dogmatic agent will fall into the 
trap whereas the switcher will be able to escape it. Similarly, an agent with self-attribution bias will update their beliefs differently from an unbiased Bayesian, leading
them to choose different gambles. I exploit such cases in order to test which model is a better fit for how subjects behave in a 
laboratory experiment. \footnote{because the setting does not match that of Heidhues et al. [2018], there will be situationf for which the theory 
does not provie a prediction. If such cases arise in the lab, they will not be used for the analysis. However, whether a misspecified 
belief persists or not for the switcher, depends highly on the realized history of signals that he gets.} In what follows I explain 
the details of how this example was implemented in the lab.

@@

# Predictions

In the example and for the seed that was drawn and fixed throughout, the models make different predictions.
